Precise Spiking Motifs in Neurobiological and Neuromorphic~Data

### 2022-12-28 brainsci-2069565_accepted.tex
finished going through all \hl

In~\citep{lagorce_hots_2017}, \textit{\hl{time surfaces}} were introduced as an event-driven 2D image of the delay between the last event recorded at the address of a pixel and the current time. An exponential decay is applied on this delay to obtain the analog values of the time surfaces. It gives more precision to represent recent events and offers an analogy with the LIF spiking neuron. It is a way to represent the local dynamics embedded in the event-based recordings, and with unsupervised learning on the event stream based on the cosine similarity, they can capture repeating motifs within the input signals. Learned time surfaces can be used for object recognition~\citep{lagorce_hots_2017, sironi_hats_2018, maro_event-based_2020, grimaldi_homeostatic_2021,grimaldi_robust_2022} and show that this method could be efficiently applied to state-of-the-art benchmarks.

@@

%
\subsection{Computations with Delays in Neuromorphic Hardware}
%
For the rest of this section, we report examples of implementations of event-based algorithms using precise spatio-temporal motifs on neuromorphic hardware. 
\citep{hussain_deltron_2012} implemented a delay-learning algorithm on an analog chip. Online learning on neuromorphic chips is still a challenge today and for this work, only the detection of spiking motifs was performed on the analog architecture; training was performed digitally and based on the tempotron learning rule~\citep{gutig_tempotron_2006}. In addition to delay learning, a group at the University of West Sydney developed a neuromorphic implementation of multiple synaptic plasticity learning rules~\citep{wang_neuromorphic_2015}. They showed that STDP and spike-timing-dependent delay plasticity rules could be implemented in both a digital and an analog chip. From the network parameters and the physical limitations to store it on-chip, they proved that the digital implementation is way easier to scale up and that an external memory would be needed for a larger network. The same group presented a FPGA hardware implementation of polychronous networks in which propagation delays are learned in a supervised manner, based on the expected firing time of the post-synaptic neuron~\citep{wang_fpga_2014}. %This paper proposes a supervised delay learning algorithm for spiking neurons with temporal encoding, in which both the weight and delay of a synaptic connection can be adjusted to enhance the learning performance. 
\citet{pfeil_neuromorphic_2013} implemented STDP on a mixed analog--digital chip to simulate the sound localization processes observed on the barn owl auditory system~\citep{gerstner_neuronal_1996}. Coherence detection on input spikes coming from two sources was obtained with a 50 \hl{$ns$} precision. They claimed that this unsupervised learning denoises the input and compensates for variations between neural components. The variability of response of the analog components can be compensated by population coding for responses robust to noise, and this phenomenon is also observed in biological neural networks~\citep{boerlin_spike-based_2011}. 
A recent work performed the implementation of a sparse vector symbol architecture binding operation on the Loihi chip, delay lines and coincidence detection, used to compute the binding operation~\citep{renner_sparse_2022}. They highlighted the fact that using delays can be expensive \add[Laurent]{notably in memory bandwidth} because incoming spikes have to be stored in blocks with a temporal dimension equivalent to the maximal delay. Note that this problem is also due to the algorithm used in this paper and that the analog chips must not suffer from this type of~limitation.

@@

 Overall, our reviewing effort has shown that a growing community is focusing on that aspect. This community is based on solid and validated evidence, which is breaking novel grounds thanks to the current technical advances. Moreover, we also showed that this community is highly diverse, operating on {\hl{in vivo}}, {\hl{in computo}} and {\hl{in silico}} systems. As a consequence, the global effort is still largely scattered, which limits its larger acceptance in~neuroscience.

@@

\funding{
This research was funded by the European Union ERA-NET CHIST-ERA 2018 research and innovation program under grant number ANR-19-CHR3-0008-03 (``\href{http://aprovis3d.eu/}{\hl{APROVIS3D}}''). % Agence Nationale de la Recherche %HL and 
LP, CB and AG received funding from the ANR grant number ANR-20-CE23-0021 ``\href{https://laurentperrinet.github.io/grant/anr-anr/}{\hl{AgileNeuroBot}}''.
% LP received funding 
LP received support from the french government under the France 2030 investment plan, as part of the Initiative d’Excellence d’Aix-Marseille Université – A*MIDEX number AMX-21-RID-025 ``\href{https://laurentperrinet.github.io/grant/polychronies/}{\hl{Polychronies}}''.}

@@

\bibitem[DeWeese and Zador(2003)]{deweese_binary_2003}
DeWeese, M.R.; Zador, A.M.
\newblock {\em Binary Coding in Auditory Cortex}; \hl{Neural Information Processing
  Systems Foundation:} %MDPI: Please add the location of the publisher (City and Country).
   2003.

@@

\bibitem[DiLorenzo and Victor(2013)]{dilorenzo_spike_2013}
DiLorenzo, P.M.; Victor, J.D.
\newblock {\em Spike {Timing}: {Mechanisms} and {Function}}; CRC Press:  \hl{Boca Raton, FL, USA,} %newly added information, please confirm
  2013.
%\newblock Google-Books-ID: KTHUIMUpQCUC.  %MDPI: We removed Google-Books-ID: KTHUIMUpQCUC. Please confirm this revision.

@@

\bibitem[Flourens(1842)]{flourens_recherches_1842}
Flourens, M.J.P.
\newblock {\em Recherches Expérimentales sur les Propriétés et les Fonctions
  du Système Nerveux, Dans les Animaux Vertébrés}; Balliere, J.-B., Ed.;  \hl{1842.} %MDPI: Please add the name of the publisher and their location.

@@

\bibitem[Nowak and Bullier(1997)]{nowak_timing_1997}
Nowak, L.G.; Bullier, J.
\newblock The {Timing} of {Information} {Transfer} in the {Visual} {System}. In
  {\em Extrastriate {Cortex} in {Primates}}; Springer: \hl{Boston, MA, USA,} %MDPI: We added the location of the publisher. Please confirm.
  1997; pp. 205--241.

@@

\bibitem[Paugam-Moisy and Bohte(2012)]{paugam-moisy_computing_2012}
Paugam-Moisy, H.; Bohte, S.M.
\newblock Computing with spiking neuron networks. In {\em Handbook of Natural
  Computing}; Springer:  \hl{Berlin/Heidelberg, Germany,} %newly added information, please confirm
  2012.

@@

\bibitem[Deneve(2004)]{deneve_bayesian_2004}
Deneve, S.
\newblock Bayesian inference in spiking neurons.
\newblock In \emph{Proceedings of the Advances in {Neural} {Information} {Processing}
  {Systems}}; MIT Press:  \hl{Cambridge, MA, USA,} %newly added information, please confirm
  2004, Volume~17.

@@

\bibitem[Berry(2022)]{berry_spike_2022}
Puchalla, J.; Berry, M.J.
\newblock \emph{Spike {Trains} of {Retinal} {Ganglion} {Cells} {Viewing} a {Repeated}
  {Natural} {Movie}}; \hl{Princeton University: Princeton, NJ, USA,} %MDPI: We added the name of the publisher and location. Please confirm.
  {2022}.
\newblock {{https://doi.org/10.34770/V0V4-3H52}}.

@@

\bibitem[Cleland(2014)]{cleland_construction_2014}
Cleland, T.A.
\newblock Construction of {Odor} {Representations} by {Olfactory} {Bulb}
  {Microcircuits}. In {\em Progress in {Brain} {Research}}; Elsevier:  \hl{Amsterdam, The Netherlands,} %newly added information, please confirm
  2014;
  Volume 208, pp. 177--203.
\newblock {{https://doi.org/10.1016/B978-0-444-63350-7.00007-3}}.

@@

\bibitem[Simoncelli {et~al.}(2003)Simoncelli, Paninski, Pillow, and
  Schwartz]{simoncelli_characterization_2003}
Simoncelli, E.P.; Paninski, L.; Pillow, J.; Schwartz, O.
\newblock Characterization of {Neural} {Responses} with {Stochastic} {Stimuli}. In \emph{\hl{The New Cognitive Neurosciences}}, \hl{3rd ed.; Gazzaniga, M., Ed.; MIT Press: Cambridge, MA, USA,} %MDPI: Newly added  information. Please confirm.
  {2003}.

@@

\bibitem[Kohn and Smith(2016)]{kohn_utah_2016}
Kohn, A.; Smith, M.
\newblock Utah Array Extracellular Recordings of Spontaneous and Visually
  Evoked Activity from Anesthetized Macaque Primary Visual Cortex ({V1}). 
  2016.   
Available online: {\url{https://doi.org/10.6080/K0NC5Z4X}}  \hl{(accessed on date month year).} %MDPI: Please add the access date (format: Date Month Year), e.g., accessed on 1 January 2020.

@@

\bibitem[Grün {et~al.}(2010)Grün, Diesmann, and
  Aertsen]{grun_unitary_2010}
Grün, S.; Diesmann, M.; Aertsen, A.
\newblock Unitary {Event} {Analysis}. In {\em Analysis of {Parallel} {Spike}
  {Trains}}; Springer: \hl{Boston, MA, USA,} %MDPI: We added the location of the publisher. Please confirm.
  2010; pp. 191--220.

@@

\bibitem[Stringer(2020)]{stringer_mouselandrastermap_2020}
Stringer, C.
\newblock {MouseLand}/Rastermap: {A} Multi-Dimensional Embedding Algorithm.
  \hl{2020}. %MDPI: Please add website and access date. Please check.

@@

\bibitem[Grimaldi and Perrinet(2022)]{grimaldi_learning_2022}
Grimaldi, A.; Perrinet, L.U.
\newblock Learning hetero-synaptic delays for motion detection in a single
  layer of spiking neurons.
\newblock In Proceedings of the 2022 {IEEE} {International} {Conference} on
  {Image} {Processing} ({ICIP}), \hl{Bordeaux, France, 16--19 October} %MDPI: We added the location and date of the conference. Please confirm.
 2022; pp.~3591--3595.
%\newblock ISSN: 2381-8549,
  {{https://doi.org/10.1109/ICIP46576.2022.9897394}}.

\bibitem[Madadi~Asl and
  Ramezani~Akbarabadi(2022)]{madadi_asl_delay-dependent_2022}
Madadi~Asl, M.; Ramezani~Akbarabadi, S.
\newblock Delay-dependent transitions of phase synchronization and coupling
  symmetry between neurons shaped by spike-timing-dependent plasticity.
\newblock {\em Cogn. Neurodynamics} {\bf \hl{2022} %MDPI: Please add the volume.
}, 1--14.
\newblock {{https://doi.org/10.1007/s11571-022-09850-x}}.

@@

\bibitem[Datadien {et~al.}(2011)Datadien, Haselager, and
  Sprinkhuizen-Kuyper]{datadien_right_2011}
Datadien, A.; Haselager, P.; Sprinkhuizen-Kuyper, I.
\newblock {\em The {Right} {Delay}---{Detecting} {Specific} {Spike} {Patterns}
  with {STDP} and {Axonal} {Conduction} {Delays}}; \hl{Springer:  Berlin/Heidelberg, Germany,} %MDPI: We added the name of the publisher and location. Please confirm.
 2011;
\newblock pp. 90--99.

@@

\bibitem[Luo {et~al.}(2022)Luo, Qu, Wang, Yi, Zhang, and
  Zhang]{luo_supervised_2022}
Luo, X.; Qu, H.; Wang, Y.; Yi, Z.; Zhang, J.; Zhang, M.
\newblock Supervised {Learning} in {Multilayer} {Spiking} {Neural} {Networks}
  {With} {Spike} {Temporal} {Error} {Backpropagation}.
\newblock {\em IEEE Trans. Neural Netw. Learn. Syst.} {\bf
  \hl{2022} %MDPI: Please add the volume.
}, 1--13.
\newblock {{https://doi.org/10.1109/tnnls.2022.3164930}}.

@@

\bibitem[Diesmann and Gewaltig(2003)]{diesmann_nest_2003}
Diesmann, M.; Gewaltig, M.O.
\newblock {NEST}: {An} {Environment} for {Neural} {Systems} {Simulations}.
\newblock {\em GWDG-Bericht Nr. 58 Theo Plesser, Volker Macho (Hrsg.)}; {
  \hl{2003}}; %MDPI: Please add the name of the publisher and their location.
 p.~29.

@@

\bibitem[Mead and Ismail(1989)]{mead_analog_1989}
Mead, C.; Ismail, M.
\newblock {\em Analog {VLSI} {Implementation} of {Neural} {Systems}}; Springer
  Science \& Business Media:  \hl{Berlin/Heidelberg, Germany,} %newly added information, please confirm
  1989.
%\newblock Google-Books-ID: 9e29dOiXeiMC.

@@

\bibitem[Furber and Bogdan(2020)]{furber_spinnaker_2020}
Furber, S.; Bogdan, P., Eds.
\newblock {\em {SpiNNaker}: {A} {Spiking} {Neural} {Network} {Architecture}};
  Now Publishers: \hl{Norwell, MA, USA,} %MDPI: We added the location of the publisher. Please confirm.
  2020.
\newblock {{https://doi.org/10.1561/9781680836523}}.

@@

\bibitem[Schemmel {et~al.}(2010)Schemmel, Brüderle, Grübl, Hock, Meier,
  and Millner]{schemmel_wafer-scale_2010}
Schemmel, J.; Brüderle, D.; Grübl, A.; Hock, M.; Meier, K.; Millner, S.
\newblock A wafer-scale neuromorphic hardware system for large-scale neural
  modeling.
\newblock In Proceedings of the 2010 {IEEE} {International} {Symposium} on
  {Circuits} and {Systems} ({ISCAS}), \hl{Paris, France, 30 May--2 June} %MDPI: We added the location and date of the conference. Please confirm.
 2010; pp. 1947--1950.
{{https://doi.org/10.1109/ISCAS.2010.5536970}}.

@@

\bibitem[Farquhar {et~al.}(2006)Farquhar, Gordon, and
  Hasler]{farquhar_field_2006}
Farquhar, E.; Gordon, C.; Hasler, P.
\newblock A {Field} {Programmable} {Neural} {Array}.
\newblock In Proceedings of the 2006 {IEEE} {International} {Symposium} on
  {Circuits} and {Systems}, \hl{Kos, Greece, 21--24 May} %MDPI: We added the location and date of the conference. Please confirm.
 2006; pp. 4114--4117.
\newblock {{https://doi.org/10.1109/ISCAS.2006.1693534}}.

@@

\bibitem[Sironi {et~al.}(2018)Sironi, Brambilla, Bourdis, Lagorce, and
  Benosman]{sironi_hats_2018}
Sironi, A.; Brambilla, M.; Bourdis, N.; Lagorce, X.; Benosman, R.
\newblock {HATS}: {Histograms} of {Averaged} {Time} {Surfaces} for {Robust}
  {Event}-{Based} {Object} {Classification}.
\newblock In Proceedings of the 2018 {IEEE}/{CVF} {Conference} on {Computer}
  {Vision} and {Pattern} {Recognition}, Salt Lake City, UT, USA, \hl{18--23 June} %MDPI: We added the  date of the conference. Please confirm.
  2018;
  pp. 1731--1740.
\newblock {{https://doi.org/10.1109/CVPR.2018.00186}}.

@@

\bibitem[Grimaldi {et~al.}(2021)Grimaldi, Boutin, Perrinet, Ieng, and
  Benosman]{grimaldi_homeostatic_2021}
Grimaldi, A.; Boutin, V.; Perrinet, L.; Ieng, S.H.; Benosman, R.
\newblock A homeostatic gain control mechanism to improve event-driven object
  recognition.
\newblock In Proceedings of the 2021 {International} {Conference} on
  {Content}-{Based} {Multimedia} {Indexing} ({CBMI}),  \hl{Lille, France,  28--30 June} %MDPI: We added the location and date of the conference. Please confirm.
  2021.
\newblock {{https://doi.org/10.1109/cbmi50038.2021.9461901}}.

@@

\bibitem[Stoffregen {et~al.}(2019)Stoffregen, Gallego, Drummond, Kleeman,
  and Scaramuzza]{stoffregen_event-based_2019}
Stoffregen, T.; Gallego, G.; Drummond, T.; Kleeman, L.; Scaramuzza, D.
\newblock Event-{Based} {Motion} {Segmentation} by {Motion} {Compensation}.
\newblock In Proceedings of the 2019 {IEEE}/{CVF} {International} {Conference}
  on {Computer} {Vision} ({ICCV}), \hl{Seoul, Republic of Korea, 27 February} %MDPI: We added the location and date of the conference. Please confirm.
 2019; pp. 7243--7252.
 {{https://doi.org/10.1109/ICCV.2019.00734}}.

@@

\bibitem[Hussain {et~al.}(2012)Hussain, Basu, Wang, and
  Hamilton]{hussain_deltron_2012}
Hussain, S.; Basu, A.; Wang, M.; Hamilton, T.J.
\newblock {DELTRON}: {Neuromorphic} architectures for delay based learning.
\newblock In Proceedings of the 2012 {IEEE} {Asia} {Pacific} {Conference} on
  {Circuits} and {Systems},  \hl{Kaohsiung, Taiwan, 2--5 December} %MDPI: We added the location and date of the conference. Please confirm.
 2012; pp. 304--307.
\newblock {{https://doi.org/10.1109/APCCAS.2012.6419032}}.

@@

\bibitem[Wang {et~al.}(2014)Wang, Hamilton, Tapson, and van
  Schaik]{wang_fpga_2014}
Wang, R.; Hamilton, T.J.; Tapson, J.; van Schaik, A.
\newblock An {FPGA} design framework for large-scale spiking neural networks.
\newblock In Proceedings of the 2014 {IEEE} {International} {Symposium} on
  {Circuits} and {Systems} ({ISCAS}), \hl{Melbourne, VIC, Australia, 1--5 June} %MDPI: We added the location and date of the conference. Please confirm.
 2014; pp. 457--460.
 {{https://doi.org/10.1109/ISCAS.2014.6865169}}.

>>>>

In~\citep{lagorce_hots_2017}, time surfaces were introduced as an event-driven 2D image of the delay between the last event recorded at the address of a pixel and the current time. An exponential decay is applied on this delay to obtain the analog values of the time surfaces. It gives more precision to represent recent events and offers an analogy with the LIF spiking neuron. It is a way to represent the local dynamics embedded in the event-based recordings, and with unsupervised learning on the event stream based on the cosine similarity, they can capture repeating motifs within the input signals. Learned time surfaces can be used for object recognition~\citep{lagorce_hots_2017, sironi_hats_2018, maro_event-based_2020, grimaldi_homeostatic_2021,grimaldi_robust_2022} and show that this method could be efficiently applied to state-of-the-art benchmarks.

@@

%
\subsection{Computations with Delays in Neuromorphic Hardware}
%
For the rest of this section, we report examples of implementations of event-based algorithms using precise spatio-temporal motifs on neuromorphic hardware. 
\citep{hussain_deltron_2012} implemented a delay-learning algorithm on an analog chip. Online learning on neuromorphic chips is still a challenge today and for this work, only the detection of spiking motifs was performed on the analog architecture; training was performed digitally and based on the tempotron learning rule~\citep{gutig_tempotron_2006}. In addition to delay learning, a group at the University of West Sydney developed a neuromorphic implementation of multiple synaptic plasticity learning rules~\citep{wang_neuromorphic_2015}. They showed that STDP and spike-timing-dependent delay plasticity rules could be implemented in both a digital and an analog chip. From the network parameters and the physical limitations to store it on-chip, they proved that the digital implementation is way easier to scale up and that an external memory would be needed for a larger network. The same group presented a FPGA hardware implementation of polychronous networks in which propagation delays are learned in a supervised manner, based on the expected firing time of the post-synaptic neuron~\citep{wang_fpga_2014}. %This paper proposes a supervised delay learning algorithm for spiking neurons with temporal encoding, in which both the weight and delay of a synaptic connection can be adjusted to enhance the learning performance. 
\citet{pfeil_neuromorphic_2013} implemented STDP on a mixed analog--digital chip to simulate the sound localization processes observed on the barn owl auditory system~\citep{gerstner_neuronal_1996}. Coherence detection on input spikes coming from two sources was obtained with a 50 $ns$ precision. They claimed that this unsupervised learning denoises the input and compensates for variations between neural components. The variability of response of the analog components can be compensated by population coding for responses robust to noise, and this phenomenon is also observed in biological neural networks~\citep{boerlin_spike-based_2011}. 
A recent work performed the implementation of a sparse vector symbol architecture binding operation on the Loihi chip, delay lines and coincidence detection, used to compute the binding operation~\citep{renner_sparse_2022}. They highlighted the fact that using delays can be expensive \add[Laurent]{notably in memory bandwidth} because incoming spikes have to be stored in blocks with a temporal dimension equivalent to the maximal delay. Note that this problem is also due to the algorithm used in this paper and that the analog chips must not suffer from this type of~limitation.

@@

 Overall, our reviewing effort has shown that a growing community is focusing on that aspect. This community is based on solid and validated evidence, which is breaking novel grounds thanks to the current technical advances. Moreover, we also showed that this community is highly diverse, operating in biology, computational neuroscience or neuromorphic engineering. As a consequence, the global effort is still largely scattered, which limits its larger acceptance in~neuroscience.

@@

\funding{
This research was funded by the European Union ERA-NET CHIST-ERA 2018 research and innovation program under grant number ANR-19-CHR3-0008-03 (``\href{http://aprovis3d.eu/}{APROVIS3D}''). % Agence Nationale de la Recherche %HL and 
LP, CB and AG received funding from the ANR grant number ANR-20-CE23-0021 ``\href{https://laurentperrinet.github.io/grant/anr-anr/}{AgileNeuroBot}''.
% LP received funding  
LP received support from the french government under the France 2030 investment plan, as part of the Initiative d’Excellence d’Aix-Marseille Université – A*MIDEX number AMX-21-RID-025 ``\href{https://laurentperrinet.github.io/grant/polychronies/}{Polychronies}''.}

@@

\bibitem[DeWeese and Zador(2003)]{deweese_binary_2003}
DeWeese, M.R.; Zador, A.M.
\newblock {\em Binary Coding in Auditory Cortex}; {Neural Information Processing
  Systems Foundation:} 
  \newblock MIT Press: Cambridge, MA, USA,
  %MDPI: Please add the location of the publisher (City and Country).
   2003.

@@

\bibitem[DiLorenzo and Victor(2013)]{dilorenzo_spike_2013}
DiLorenzo, P.M.; Victor, J.D.
\newblock {\em Spike {Timing}: {Mechanisms} and {Function}}; CRC Press:  {Boca Raton, FL, USA,} %newly added information, please confirm
  2013.
%\newblock Google-Books-ID: KTHUIMUpQCUC.  %MDPI: We removed Google-Books-ID: KTHUIMUpQCUC. Please confirm this revision.

@@

\bibitem[Flourens(1842)]{flourens_recherches_1842}
Flourens, M.J.P.
\newblock {\em Recherches Expérimentales sur les Propriétés et les Fonctions
  du Système Nerveux, Dans les Animaux Vertébrés}; Hachette {BNF}: {Paris, France,} {1842.} %MDPI: Please add the name of the publisher and their location.

@@

\bibitem[Nowak and Bullier(1997)]{nowak_timing_1997}
Nowak, L.G.; Bullier, J.
\newblock The {Timing} of {Information} {Transfer} in the {Visual} {System}. In
  {\em Extrastriate {Cortex} in {Primates}}; Springer: {Boston, MA, USA,} %MDPI: We added the location of the publisher. Please confirm.
  1997; pp. 205--241.

@@

\bibitem[Paugam-Moisy and Bohte(2012)]{paugam-moisy_computing_2012}
Paugam-Moisy, H.; Bohte, S.M.
\newblock Computing with spiking neuron networks. In {\em Handbook of Natural
  Computing}; Springer:  {Berlin/Heidelberg, Germany,} %newly added information, please confirm
  2012.

@@

\bibitem[Deneve(2004)]{deneve_bayesian_2004}
Deneve, S.
\newblock Bayesian inference in spiking neurons.
\newblock In \emph{Proceedings of the Advances in {Neural} {Information} {Processing}
  {Systems}}; MIT Press: Cambridge, MA, USA, %newly added information, please confirm
  2004, Volume~17.

@@

\bibitem[Berry(2022)]{berry_spike_2022}
Puchalla, J.; Berry, M.J.
\newblock \emph{Spike {Trains} of {Retinal} {Ganglion} {Cells} {Viewing} a {Repeated}
  {Natural} {Movie}}; {Princeton University: Princeton, NJ, USA,} %MDPI: We added the name of the publisher and location. Please confirm.
  {2022}.
\newblock {{https://doi.org/10.34770/V0V4-3H52}}.

@@

\bibitem[Cleland(2014)]{cleland_construction_2014}
Cleland, T.A.
\newblock Construction of {Odor} {Representations} by {Olfactory} {Bulb}
  {Microcircuits}. In {\em Progress in {Brain} {Research}}; Elsevier:  {Amsterdam, The Netherlands,} %newly added information, please confirm
  2014;
  Volume 208, pp. 177--203.
\newblock {{https://doi.org/10.1016/B978-0-444-63350-7.00007-3}}.

@@

\bibitem[Simoncelli {et~al.}(2003)Simoncelli, Paninski, Pillow, and
  Schwartz]{simoncelli_characterization_2003}
Simoncelli, E.P.; Paninski, L.; Pillow, J.; Schwartz, O.
\newblock Characterization of {Neural} {Responses} with {Stochastic} {Stimuli}. In \emph{{The New Cognitive Neurosciences}}, {3rd ed.; Gazzaniga, M., Ed.; MIT Press: Cambridge, MA, USA,} %MDPI: Newly added  information. Please confirm.
  {2003}.

@@

\bibitem[Kohn and Smith(2016)]{kohn_utah_2016}
Kohn, A.; Smith, M.
\newblock Utah Array Extracellular Recordings of Spontaneous and Visually
  Evoked Activity from Anesthetized Macaque Primary Visual Cortex ({V1}). 
  2016.   
Available online: {\url{https://doi.org/10.6080/K0NC5Z4X}}  {(accessed on 25 December 2022).} %MDPI: Please add the access date (format: Date Month Year), e.g., accessed on 1 January 2020.

@@

\bibitem[Grün {et~al.}(2010)Grün, Diesmann, and
  Aertsen]{grun_unitary_2010}
Grün, S.; Diesmann, M.; Aertsen, A.
\newblock Unitary {Event} {Analysis}. In {\em Analysis of {Parallel} {Spike}
  {Trains}}; Springer: {Boston, MA, USA,} %MDPI: We added the location of the publisher. Please confirm.
  2010; pp. 191--220.

@@

\bibitem[Stringer(2020)]{stringer_mouselandrastermap_2020}
Stringer, C.
\newblock {MouseLand}/Rastermap: {A} Multi-Dimensional Embedding Algorithm.
  {2020}. %MDPI: Please add website and access date. Please check.
  Available online: {\url{https://github.com/MouseLand/rastermap}}  {(accessed on 25 December 2022).} %MDPI: Please add the access date (format: Date Month Year), e.g., accessed on 1 January 2020.

@@

\bibitem[Grimaldi and Perrinet(2022)]{grimaldi_learning_2022}
Grimaldi, A.; Perrinet, L.U.
\newblock Learning hetero-synaptic delays for motion detection in a single
  layer of spiking neurons.
\newblock In Proceedings of the 2022 {IEEE} {International} {Conference} on
  {Image} {Processing} ({ICIP}), {Bordeaux, France, 16--19 October} %MDPI: We added the location and date of the conference. Please confirm.
 2022; pp.~3591--3595.
%\newblock ISSN: 2381-8549,
  {{https://doi.org/10.1109/ICIP46576.2022.9897394}}.

\bibitem[Madadi~Asl and
  Ramezani~Akbarabadi(2022)]{madadi_asl_delay-dependent_2022}
Madadi~Asl, M.; Ramezani~Akbarabadi, S.
\newblock Delay-dependent transitions of phase synchronization and coupling
  symmetry between neurons shaped by spike-timing-dependent plasticity.
\newblock {\em Cogn. Neurodynamics} {\bf {2022} %MDPI: Please add the volume. There is none for this citation
}, 1--14.
\newblock {{https://doi.org/10.1007/s11571-022-09850-x}}.

@@

\bibitem[Datadien {et~al.}(2011)Datadien, Haselager, and
  Sprinkhuizen-Kuyper]{datadien_right_2011}
Datadien, A.; Haselager, P.; Sprinkhuizen-Kuyper, I.
\newblock {\em The {Right} {Delay}---{Detecting} {Specific} {Spike} {Patterns}
  with {STDP} and {Axonal} {Conduction} {Delays}}; {Springer:  Berlin/Heidelberg, Germany,} %MDPI: We added the name of the publisher and location. Please confirm.
 2011;
\newblock pp. 90--99.

@@

\bibitem[Luo {et~al.}(2022)Luo, Qu, Wang, Yi, Zhang, and
  Zhang]{luo_supervised_2022}
Luo, X.; Qu, H.; Wang, Y.; Yi, Z.; Zhang, J.; Zhang, M.
\newblock Supervised {Learning} in {Multilayer} {Spiking} {Neural} {Networks}
  {With} {Spike} {Temporal} {Error} {Backpropagation}.
\newblock {\em IEEE Trans. Neural Netw. Learn. Syst.} {\bf
  {2022} %MDPI: Please add the volume. No volume for this citation
}, 1--13.
\newblock {{https://doi.org/10.1109/tnnls.2022.3164930}}.

@@

\bibitem[Diesmann and Gewaltig(2003)]{diesmann_nest_2003}
Diesmann, M.; Gewaltig, M.O.
\newblock {NEST}: {An} {Environment} for {Neural} {Systems} {Simulations}.
\newblock {\em GWDG-Bericht Nr. 58 Theo Plesser, Volker Macho (Hrsg.)}; {
  {2003}}; %MDPI: Please add the name of the publisher and their location. This is a tech report
 p.~29.

@@

\bibitem[Mead and Ismail(1989)]{mead_analog_1989}
Mead, C.; Ismail, M.
\newblock {\em Analog {VLSI} {Implementation} of {Neural} {Systems}}; Springer
  Science \& Business Media:  {Berlin/Heidelberg, Germany,} %newly added information, please confirm
  1989.
%\newblock Google-Books-ID: 9e29dOiXeiMC.

@@

\bibitem[Furber and Bogdan(2020)]{furber_spinnaker_2020}
Furber, S.; Bogdan, P., Eds.
\newblock {\em {SpiNNaker}: {A} {Spiking} {Neural} {Network} {Architecture}};
  Now Publishers: {Norwell, MA, USA,} %MDPI: We added the location of the publisher. Please confirm.
  2020.
\newblock {{https://doi.org/10.1561/9781680836523}}.

@@

\bibitem[Schemmel {et~al.}(2010)Schemmel, Brüderle, Grübl, Hock, Meier,
  and Millner]{schemmel_wafer-scale_2010}
Schemmel, J.; Brüderle, D.; Grübl, A.; Hock, M.; Meier, K.; Millner, S.
\newblock A wafer-scale neuromorphic hardware system for large-scale neural
  modeling.
\newblock In Proceedings of the 2010 {IEEE} {International} {Symposium} on
  {Circuits} and {Systems} ({ISCAS}), {Paris, France, 30 May--2 June} %MDPI: We added the location and date of the conference. Please confirm.
 2010; pp. 1947--1950.
{{https://doi.org/10.1109/ISCAS.2010.5536970}}.

@@

\bibitem[Farquhar {et~al.}(2006)Farquhar, Gordon, and
  Hasler]{farquhar_field_2006}
Farquhar, E.; Gordon, C.; Hasler, P.
\newblock A {Field} {Programmable} {Neural} {Array}.
\newblock In Proceedings of the 2006 {IEEE} {International} {Symposium} on
  {Circuits} and {Systems}, {Kos, Greece, 21--24 May} %MDPI: We added the location and date of the conference. Please confirm.
 2006; pp. 4114--4117.
\newblock {{https://doi.org/10.1109/ISCAS.2006.1693534}}.

@@

\bibitem[Sironi {et~al.}(2018)Sironi, Brambilla, Bourdis, Lagorce, and
  Benosman]{sironi_hats_2018}
Sironi, A.; Brambilla, M.; Bourdis, N.; Lagorce, X.; Benosman, R.
\newblock {HATS}: {Histograms} of {Averaged} {Time} {Surfaces} for {Robust}
  {Event}-{Based} {Object} {Classification}.
\newblock In Proceedings of the 2018 {IEEE}/{CVF} {Conference} on {Computer}
  {Vision} and {Pattern} {Recognition}, Salt Lake City, UT, USA, {18--23 June} %MDPI: We added the  date of the conference. Please confirm.
  2018;
  pp. 1731--1740.
\newblock {{https://doi.org/10.1109/CVPR.2018.00186}}.

@@

\bibitem[Grimaldi {et~al.}(2021)Grimaldi, Boutin, Perrinet, Ieng, and
  Benosman]{grimaldi_homeostatic_2021}
Grimaldi, A.; Boutin, V.; Perrinet, L.; Ieng, S.H.; Benosman, R.
\newblock A homeostatic gain control mechanism to improve event-driven object
  recognition.
\newblock In Proceedings of the 2021 {International} {Conference} on
  {Content}-{Based} {Multimedia} {Indexing} ({CBMI}), {Lille, France,  28--30 June} %MDPI: We added the location and date of the conference. Please confirm.
  2021.
\newblock {{https://doi.org/10.1109/cbmi50038.2021.9461901}}.

@@

\bibitem[Stoffregen {et~al.}(2019)Stoffregen, Gallego, Drummond, Kleeman,
  and Scaramuzza]{stoffregen_event-based_2019}
Stoffregen, T.; Gallego, G.; Drummond, T.; Kleeman, L.; Scaramuzza, D.
\newblock Event-{Based} {Motion} {Segmentation} by {Motion} {Compensation}.
\newblock In Proceedings of the 2019 {IEEE}/{CVF} {International} {Conference}
  on {Computer} {Vision} ({ICCV}), {Seoul, Republic of Korea, 27 February} %MDPI: We added the location and date of the conference. Please confirm.
 2019; pp. 7243--7252.
 {{https://doi.org/10.1109/ICCV.2019.00734}}.

@@

\bibitem[Hussain {et~al.}(2012)Hussain, Basu, Wang, and
  Hamilton]{hussain_deltron_2012}
Hussain, S.; Basu, A.; Wang, M.; Hamilton, T.J.
\newblock {DELTRON}: {Neuromorphic} architectures for delay based learning.
\newblock In Proceedings of the 2012 {IEEE} {Asia} {Pacific} {Conference} on
  {Circuits} and {Systems},  {Kaohsiung, Taiwan, 2--5 December} %MDPI: We added the location and date of the conference. Please confirm.
 2012; pp. 304--307.
\newblock {{https://doi.org/10.1109/APCCAS.2012.6419032}}.

@@

\bibitem[Wang {et~al.}(2014)Wang, Hamilton, Tapson, and van
  Schaik]{wang_fpga_2014}
Wang, R.; Hamilton, T.J.; Tapson, J.; van Schaik, A.
\newblock An {FPGA} design framework for large-scale spiking neural networks.
\newblock In Proceedings of the 2014 {IEEE} {International} {Symposium} on
  {Circuits} and {Systems} ({ISCAS}), {Melbourne, VIC, Australia, 1--5 June} %MDPI: We added the location and date of the conference. Please confirm.
 2014; pp. 457--460.
 {{https://doi.org/10.1109/ISCAS.2014.6865169}}.

\bibitem[Pfeil {et~al.}(2013)Pfeil, Scherzer, Schemmel, and
  Meier]{pfeil_neuromorphic_2013}
Pfeil, T.; Scherzer, A.C.; Schemmel, J.; Meier, K.
\newblock Neuromorphic learning towards nano second precision.
\newblock In Proceedings of the The 2013 {International} {Joint} {Conference}
  on {Neural} {Networks} ({IJCNN}), {Dallas, TX, USA, 4--9 August} %MDPI: We added the location and date of the conference. Please confirm.
 2013; pp. 1--5.
 {{https://doi.org/10.1109/IJCNN.2013.6706828}}.
